Extending Height Above Nearest Drainage to Model Multiple Fluvial Sources in Flood Inundation Mapping Applications for the U.S. National Water Model

### 2022-08-31 manuscripts/owp_fim4_2022/owp_fim4_expanded.tex
* updated references * updated affiliations
* update WRF reference

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
%
%
\authors{Fernando Aristizabal\affil{1,2,3}, Fernando Salas\affil{3}, Gregory Petrochenkov\affil{4}, Trevor Grout\affil{1,3}, Brian Avant\affil{1,3}, Bradford Bates\affil{1,3}, Ryan Spies\affil{1,3}, Nick Chadwick\affil{3}, Zachary Wills\affil{3,5}, Jasmeet Judge\affil{2}}
%
%
\affiliation{1}{Lynker, Leesburg, VA, USA}
\affiliation{2}{Center for Remote Sensing, Agricultural and Biological Engineering Department, University of Florida, Gainesville, FL, USA}
\affiliation{3}{National Water Center, Office of Water Prediction, National Weather Service, National Oceanic and Atmospheric Administration, Tuscaloosa, AL, USA}
\affiliation{4}{New York Water Science Center, Hydrologic Applied Innovations Lab, United States Geological Survey, Troy, NY, USA}
\affiliation{5}{Cooperative Institute for Satellite Earth System Studies, University of Maryland, College Park, MD, USA}
%
%(repeat as many times as is necessary)
%
%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

@@

In response to growing stakeholder demand for enhanced and integrated water resource forecasts, the Office of Water Prediction (OWP) at the National Water Center (NWC) along with its partners at the National Center for Atmospheric Research (NCAR) have developed and implemented operationally the NWM which is a configuration of the Weather Research and Forecasting Hydrologic Model (WRF-Hydro) \cite{gochis2018wrf,cosgrove2019evolution}. 

@@

The NWM provides stream forecasts at these hydrofabric segments using the Muskingum-Cunge method to reduce computational requirements of a continental scale model but fails to consider backwater dynamics \cite{bedient2008hydrology,ponce1994variable,gochis2018wrf}.

>>>>

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}
%
%
\authors{Fernando Aristizabal\affil{1,2,3}, Fernando Salas\affil{3}, Gregory Petrochenkov\affil{4}, Trevor Grout\affil{1,3}, Brian Avant\affil{1,3}, Bradford Bates\affil{1,3}, Ryan Spies\affil{1,3}, Nick Chadwick\affil{3}, Zachary Wills\affil{3,5}, Jasmeet Judge\affil{2}}
%
%
\affiliation{1}{Lynker, Leesburg, VA, USA}
\affiliation{2}{Center for Remote Sensing, Agricultural and Biological Engineering Department, University of Florida, Gainesville, FL, USA}
\affiliation{3}{National Water Center, Office of Water Prediction, National Weather Service, National Oceanic and Atmospheric Administration, Tuscaloosa, AL, USA}
\affiliation{4}{Hydrologic Applied Innovations Lab, New York Water Science Center, United States Geological Survey, Troy, NY, USA}
\affiliation{5}{Cooperative Institute for Satellite Earth System Studies, University of Maryland, College Park, MD, USA}
%
%(repeat as many times as is necessary)
%
%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

@@

In response to growing stakeholder demand for enhanced and integrated water resource forecasts, the Office of Water Prediction (OWP) at the National Water Center (NWC) along with its partners at the National Center for Atmospheric Research (NCAR) have developed and implemented operationally the NWM which is a configuration of the Weather Research and Forecasting Hydrologic Model (WRF-Hydro) \cite{salas2018towards,gochis2021wrf,cosgrove2019evolution}. 

@@

The NWM provides stream forecasts at these hydrofabric segments using the Muskingum-Cunge method to reduce computational requirements of a continental scale model but fails to consider backwater dynamics \cite{bedient2008hydrology,ponce1994variable,gochis2021wrf}.
